Experiment 3 of 4

### 2017-05-16 experiments/e3/writeup/e3.Rmd
reworked

```{r rtplotHmisc, fig.width=7, fig.height=3}
# n.b. rtdata has been trimmed at 2.5 sd: use rawdata if you want untrimmed data
rawdata$Condition <- as.factor(paste(sep=' ', rawdata$Selection, rawdata$Vagueness))
ggplot(rawdata, aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition)) + 
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(0.2)) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  facet_grid(~Selection)

  mapping = aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition),
  stat = stat_summary(fun.data = "mean_cl_boot") )

ggplot(mtcars) +
  geom_pointrange
+
  facet_grid(~Selection)

d <- ggplot(mtcars, aes(cyl, mpg)) 
d + stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 2)
# +
  # theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  #       legend.key = element_blank(), aspect.ratio=1,
  #       axis.text.x = element_text(angle = 45, hjust = 1),
  #       plot.background=element_rect(fill=NA, color='white')
```

>>>>

```{r rtplotHmisc, fig.width=7, fig.height=3}
# n.b. rtdata has been trimmed at 2.5 sd: use rawdata if you want untrimmed data
rawdata$Condition <- as.factor(paste(sep=' ', rawdata$Selection, rawdata$Vagueness))
ggplot(rawdata, aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition)) + 
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(0.2)) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  facet_grid(~Selection) +
  theme(
    panel.background=element_rect(fill=NA, color='black'),
    panel.grid.major=element_line(color='grey95'), 
        #panel.grid.minor = element_blank(),
        legend.key=element_blank(), 
        aspect.ratio=1,
        axis.text.x=element_text(angle = 45, hjust = 1)
        )
```
